% CS-100 Fall 2019 Guest Lecture Report
% Use this template to write a 250-word (at max.) report on the guest lecture.

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{A Talk by Dr. Bilal Siddiqui} %Title must be written exactly as specified
\author{By *Dr. Bilal Siddiqui* \\ \\ Reviewed by *Rohan Raj*} %Speaker name must be written exactly as specified

\date{11 October 2021} % Date when report was written

\begin{document}
\maketitle
He works in the Unmanned Aerial Vehicle (Drones) industry. He has 20 years of experience and has worked in several projects which includes different kinds of drones and systems, and in several places such as Woot-Tech, SUPARCO, Saudi Aerospace Technologies, DHA Suffa University, PAC Kamra, ABM Satuma, RAeS and Imech. He is currently working on his own start up of industrial drones.
\par
He shed light on the study of dynamics such as balance of forces due to their connection with drones, and that 4G technology is used for communication with the drone and GPS for tracking. 
\par
There are different kinds of drones, having different specifications, applications, benefits and drawbacks. The two common types are multicoptor and fixed wing. Multicopter is used for agricultural spraying, while fixed wing is used for surveying. However, there is also the the evolution of Vertical Take off/Land Hybrid. It is planned for delivering parcel, for companies such as foodpanda. There are many different kinds of VTOLs as well. Drones were compared with other types of drones and different modes of transport taking into account the range, payload, price, speed and cost.
\par
He talked about the scope of this industry that it is the fastest growing industry in the world from now til 2030. Due to drones, high growth is expected in many different sectors such as Agriculture, Construction Surveying and Mapping and Logistics and Delivery Services, due to the reduction in cost and time. Statistics of drone industries with high revenue growth were shown, which gave us some insight about the future of drones. However, there are challenges of flying drone in Karachi’s airspace due to many different factors such as the issue of wires and air pollution.

\section*{References}
None 
% Please provide each reference on a separate line, leave blank if none%
\end{document}
