% CS-100 Fall 2019 Guest Lecture Report
% Use this template to write a 250-word (at max.) report on the guest lecture.

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{A Talk with Mr. Waseem Khan} %Title must be written exactly as specified
\author{By *Mr. Waseem Khan* \\ \\ Reviewed by *Rohan Raj*} %Speaker name must be written exactly as specified

\date{27 September 2021} % Date when report was written

\begin{document}
\maketitle
Coding is something that is unavoidable in the field of computer science, regardless of what specific field we are working in. Nowadays, there is no more work required on requirement analysis, as companies look for certain skills sets, which includes not only coding skills but also certain soft skills.

\par
Communication is very important in this field. We should be able to communicate well with our team members, as this is required that is often required in this field. Moreover, we not only have to code but we also have to present our work. Therefore, having good presentation skills is extremely important, as presentation is often more important than the code itself. People get to know about our work depending on the way we present.
\par
In terms of communication skills, comprehension is the most challenging for many people. There are many graduates who came before abroad, which creates a cultural difference between them and the locally graduated students. Those having weak comprehension often a burden to others. Therefore, It is crucial to have good comprehension skills. Speaking skills are mostly independent of language
\par
In this field, our approach should be problem solving, regardless of the platform being used. We should be able to solve the problem no matter what language it is. Therefore, we should be able to understand different languages and because of that, we need to learn different kinds of languages.
\par
Nowadays, classical project management has become outdated and is replaced by modern project management. There are no supervisors or sheets for coding anymore. Everyone is responsible for their own mistakes, which they get to know on the spot as the system shows an error (if any) as soon as we run the program.

\section*{References}
None 
% Please provide each reference on a separate line, leave blank if none%
\end{document}
