% CS-100 Fall 2019 Guest Lecture Report
% Use this template to write a 250-word (at max.) report on the guest lecture.

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{A Talk by Ms. Rahma Mian} %Title must be written exactly as specified
\author{By Ms. Rahma Mian \\ \\ Reviewed by Rohan Raj} %Speaker name must be written exactly as specified

\date{25 October 2021} % Date when report was written

\begin{document}
\maketitle
The seminar was about Feminism and its relation to technology. It started by introducing what is feminism. The term ‘feminism’ does not have a single definition. Some of the definitions include consideration of women and minorities rights and empowering them, and movement of equality of genders. We also got to know that there are different waves of feminism, with each wave playing a different role. These waves also had different names based on their speciality. It is ultimately about power and marginality.
\par
The speaker then introduced technological terms such as science and technology. She then showed the link between feminism and technology. She told how women, gender, and feminism were related to the production of scientific knowledge. It started in the 1960s. We were then introduced to many Key theories and themes of Feminist science and tech. She then talked about how our perspective of feminism helps us understand technology better, as it tells us about the different cultures and practices associated with it. She then clarified the aims of the feminist movement.
\par
The gendering of technologies was also discussed, the different factors affecting it such as gender relations, the meaning and character of masculinity and femininity in the working machines, and the future that is being affected due to these factors, and what should be done about it.
\par
She concluded by summarizing the link between gender and technology and talking about mutual shaping. Overall, this talk made me aware that feminism was not only just about equality but also had an interesting history behind it, that it had a relation to the tech industry as well.



\section*{References}
None 
% Please provide each reference on a separate line, leave blank if none%
\end{document}
