% CS-100 Fall 2019 Guest Lecture Report
% Use this template to write a 250-word (at max.) report on the guest lecture.

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{A Talk by Mr. Usman Zuberi} %Title must be written exactly as specified
\author{By *Mr. Usman Zuberi* \\ \\ Reviewed by *Rohan Raj*} %Speaker name must be written exactly as specified

\date{18 October 2021} % Date when report was written

\begin{document}
\maketitle
He started with the situation that we currently are in, which is university life. He told us about the purpose of universities which was to teach us to study, learn, research, explore opportunities, and enhance problem-solving skills. He explained the Beta Learning Process. 
\par
He elaborated on career selection, showing the link between the university and career. The process of choosing a career involves a lot of confusion and challenges for many people. Some of the factors include re-course, noise, parents’ influence, friends circle and emerging domains. Many people tend to change their profession due to one factor or another, which causes a lot of problems such as wastage of time and effort. There are many different elements in practical life such as processes, methodologies, frameworks, and software models.
\par
The speaker shared his personal experience in different fields, in which he talked about the challenges he faced such as transitioning from one field to another, and how did he overcome those challenges, choosing the specific field he wanted to work in. He became a Project Manager as well as a Delivery Expert. 
\par
He explained the importance of learning the basics as nothing works well unless the basics are correct. He shed light on the organizations’ growing obsession with agile, the different ways to acquire that, and the requirements to ensure to be completely agile. Moreover, he pointed out the common terms and connections, and their link to our mindset. 
\par
He concluded by summarizing the journey from a bachelor life to professional life for which he said that bachelor programs provide a gateway to many different fields from which we have to select the one specific to our goals.

\section*{References}
None 
% Please provide each reference on a separate line, leave blank if none%
\end{document}
