% CS-100 Fall 2019 Guest Lecture Report
% Use this template to write a 250-word (at max.) report on the guest lecture.

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{A Talk with Mr. Zunair Haseeb Khan} %Title must be written exactly as specified
\author{By Mr. Zunair Haseeb Khan \\ \\ Reviewed by Rohan Raj} %Speaker name must be written exactly as specified

\date{13 September 2021} % Date when report was written

\begin{document}
\maketitle
The seminar consisted of many different areas. He told us about the academics such as the importance of math, by stating its link with Computer Science. He talked about the minimum CGPA that is required. He mentioned that within first two semesters, we get an idea of where do we stand in this field. He talked about the importance of algorithms, how they are designed, and its applications in machine learning and artificial intelligence.
\par
In the field of Computer Science, ideas are very important. However, it is equally important that these ideas are relevant with time. He explained the importance of evolution. As technology is constantly updating with time, our ideas should be updated as well. Otherwise, they will become obsolete. The ideas should also be practical such that they can be implemented with the resources available at that time. Ideas that solve business related issues often match up.
\par
In order to be successful, it is crucial that we find the right tools and people who can guide us towards the correct path. Mentoring is important and can be obtained from a professional, teacher, senior, fellow classmates or the internet. It is important to share and discuss ideas, the process of achieving them, their implementation in our daily life, their applications and implications.
\par
He shed light on the process of employment. Fresh graduates are asked to present their final year project. Selection is done based on the amount of effort a person is putting and the innovative ideas being presented. Having good presentation skills is equally important as having good coding skills.
\par
He enlightened us that there is a bright future of Computer Science in Pakistan due to high demand and less availability of skilled professionals, due to which, many professionals are hired from abroad, who work remotely.
\section*{References}
None 
% Please provide each reference on a separate line, leave blank if none%
\end{document}
